Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-04 summary.tex
appendix.tex

The fundamental VSI mode is characterized by a vertical velocity
perturbation with zero nodes and $\delta v_z\sim\mathrm{constant}$
near the mid-plane, and by one node in the density perturbation at the
midplane  (i.e. anti-symmetric about $z=0$).  These have been referred
to as `corrugation modes' by \cite{nelson13}, and were found to
dominate their numerical simulations, as well as that of
\cite{stoll14}. Furthermore, when computing unstable modes for a
protoplanetary disk model with thermal relaxation based on realistic
disk properties, we find the fundamental mode to be the dominant mode,
 and it is robust against boundary conditions. The fundamental mode is
 thus likely the most relevant VSI mode in protoplanetary disks.

>>>>

The fundamental VSI mode is characterized by a symmetric vertical
velocity perturbation with zero nodes and $\delta
v_z\sim\mathrm{constant}$ near the mid-plane, and by an anti-symmetric
density perturbation with one node at $z=0$.  These have been referred
to as `corrugation modes' by \cite{nelson13}, and were found to
dominate their numerical simulations, as well as that of
\cite{stoll14}. Furthermore, when computing unstable modes for a
protoplanetary disk model with thermal relaxation based on realistic
disk properties, we find the fundamental mode to be the dominant mode,
 and it is robust against boundary conditions. The fundamental mode is
 thus likely the most relevant VSI mode in protoplanetary disks.
